\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{color}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Spectral Determinants and the Riemann Zeta Function}
\author{Seyed Ali Mozhgani}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper develops a spectral framework for analyzing the Riemann zeta function using Fredholm determinants of kernel operators. We construct a family of operators \( K_s \) whose determinants \(\Xi(s) = \det(I - K_s)\) exhibit symmetry and magnitude patterns similar to \(\zeta(s)\) along the critical line. Numerical experiments and visualizations support the spectral interpretation of zeta behavior.
\end{abstract}

\tableofcontents

\section{Introduction}
We explore the use of spectral operators and Fredholm determinants to study the Riemann zeta function. The goal is to construct a numerically tractable analogue \(\Xi(s)\) that reflects key features of \(\zeta(s)\), including symmetry and zero distribution.

\section{Fredholm Determinants and Kernel Operators}
Let \( K_s \) be a compact integral operator with kernel \( K_s(x, y) \). The Fredholm determinant is defined by:
\[
\Xi(s) := \det(I - K_s)
\]
This determinant encodes spectral data and serves as a potential analogue to \(\zeta(s)\).

\section{Functional Equation and Symmetry}
We test whether \(\Xi(s)\) satisfies a symmetry analogous to the functional equation of \(\zeta(s)\):
\[
|\Xi(0.5 + it)| \approx |\Xi(0.5 - it)|
\]
Plots and numerical comparisons are used to assess this symmetry.

\section{Numerical Experiments}
We discretize \( K_s \) over a grid and compute:
\begin{itemize}
    \item Fredholm determinant \(\Xi(s)\)
    \item Spectral radius \(\rho(K_s)\)
    \item Dominant eigenvalue
    \item Symmetry plots and difference curves
\end{itemize}
All computations are performed using Python with double precision.

\section{Results and Visualization}
Figures include:
\begin{itemize}
    \item \texttt{spectral\_radius\_plot.pdf}
    \item \texttt{functional\_equation\_symmetry.pdf}
    \item \texttt{functional\_equation\_symmetry\_diff.pdf}
\end{itemize}
These plots demonstrate the alignment between \(\Xi(s)\) and \(\zeta(s)\) in magnitude and symmetry.

\section{Conclusion}
The Fredholm determinant \(\Xi(s)\) offers a promising spectral analogue to the Riemann zeta function. While no formal equivalence is claimed, numerical evidence suggests structural parallels worth further investigation.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
